Geometric models reveal behavioral and neural signatures of how naturalistic experiences are transformed into episodic memories

### 2020-08-28 paper/main.tex
YATF -- yet another typo fix

Other recent work has used HMMs to discover laten event structure in neural responses to naturalistic stimuli~\citep{BaldEtal17}.  By applying HMMs to our explicit models of stimulus and memory dynamics, we gain a more direct understanding of those state dynamics.  For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants different in the \textit{resolution} of their recounting of low-level details.  In turn, these individual behavioral differences were reflected in differences in neural activity dynamics as participants watched the television episode.

>>>>

Other recent work has used HMMs to discover laten event structure in neural responses to naturalistic stimuli~\citep{BaldEtal17}.  By applying HMMs to our explicit models of stimulus and memory dynamics, we gain a more direct understanding of those state dynamics.  For example, we found that although the events comprising each participant's recalls recapitulated the episode's essence, participants differed in the \textit{resolution} of their recounting of low-level details.  In turn, these individual behavioral differences were reflected in differences in neural activity dynamics as participants watched the television episode.
